Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ \smaller \textbf{{Shanghai version \YellowPaperVersionNumber}}

### 2025-01-16 Paper.tex
🐞 fix: Formula for initcode limit (#920)
Co-authored-by: rahul <raxhvl@users.noreply.github.com>
fix: add missing punctuation
simpler definition

\subsection{Transient Storage}
Introduced by EIP-1153 (\cite{EIP-1153}) during the Cancun update, the transient storage, formally $\boldsymbol{\theta}$, is a volatile version of the world state account storage $\boldsymbol{\sigma}[a]_s$.
It's a mapping between addresses (160-bit identifiers) and storage (another mapping between 256-bit integer values).

>>>>

\subsection{Transient Storage}
Formally defined as $\boldsymbol{\theta}$, the transient storage (EIP-1153: \cite{EIP-1153}), is a volatile version of the world state account storage $\boldsymbol{\sigma}[a]_s$.
It's a bi-dimensional mapping between addresses and storage (i.e. a mapping of mappings between addresses, storage keys, and storage values).
